### 2014-03-15 src/analysis.Rnw
remove redundant lines

%\subsection{Sampling Criteria}

% \begin{figure*}[t]
% <<x.per.sel.sample,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
% ggplot(subset(o.xp.sample, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
%   stat_boxplot(geom ='errorbar')+
%   geom_boxplot() + facet_wrap(~type) + myopts + theme(legend.position="none")
% @
% \caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
% \label{fig:xsamplesel}
% \end{figure*}
% 
% \begin{figure*}[t]
% <<x.per.sel.round,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
% ggplot(subset(o.xp.round, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
%   stat_boxplot(geom ='errorbar')+
%   geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")
% @
% \caption{The effect of round(x) reduction, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
% \label{fig:xroundsel}
% \end{figure*}
%Our experiments found that while $round(x)$ and $sample(x)$ produced relatively reasonable reduction of mutants, the $ceil(x)$ criteria failed to produce a reasonable reduction of mutants except for higher power where the reduction was some what close to that produced by $round(x)$ and $sample(x)$ (which was expected). The $R^2$ values of $ceil(x)$ were almost always lower than that produced by $round(x)$ and $sample(x)$ for similar reduction of mutants. For this reason, we do not consider this function again. However, interested parties can refer to our published data.
% ----------------------------------------------------------------------

%\subsubsection{Lines per element}
%The aim of this criteria is similar in some sense to selective mutation. While n-selective mutation ignores the most numerous mutant species, this criteria seeks to deprioritize the most complex program elements.

@@

\begin{figure*}[t]
<<x.per.sel.sample,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
ggplot(subset(o.xp.sample, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts + theme(legend.position="none") + opts(title="sample(x)")
# @
# \caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
# \label{fig:xsamplesel}
# \end{figure*}
# 
# \begin{figure*}[t]
# <<x.per.sel.round,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
ggplot(subset(o.xp.round, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")+ opts(title="sample(x)")

@@

df <- subset(o.xp.opsel, rm.operators <= 20 & reduction != Inf & type != 'operator' & (type != 'n-selection' | rm.operators < 9))
#ggplot(df, aes(rm.operators, reduction, fill=interaction(type,rm.operators), dodge=type)) +
#  stat_boxplot(geom ='errorbar')+
#  geom_boxplot() + facet_wrap(~type) + myopts +
#  #theme(legend.position="none") +
#  opts(title="opsel(x)")
qplot(rm.operators, reduction, fill=interaction(type,rm.operators), data=df, geom="boxplot", position="dodge") + theme_bw()
@
\caption{Operator selection comparison between n-selection and other selection methods in mutation reduction.  We show only up to 8-selection}
\label{fig:xroundsel}
\end{figure*}

% \begin{figure*}[t]
% <<loc.per.sel.sample,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
% ggplot(subset(o.loc.ext, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
%   stat_boxplot(geom ='errorbar')+
%   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none")
% @
% \caption{The effect of loc (external) reduction. All are above 0.98 $R^2$.}
% \label{fig:locsel}
% \end{figure*}
% 
%\begin{figure*}[t]
%<<wloc.per.sel.sample,fig.width=10, fig.height=2, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
%o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
%ggplot(subset(o.loc.int, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
%  stat_boxplot(geom ='errorbar')+
%  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none")
%@
%\caption{The effect of loc (internal) reduction. All are above 0.90 $R^2$.}
%\label{fig:wlocsel}
%\end{figure*}
%
%
%The results of this selection criteria are provided in Table~\ref{tbl:locsel}. The effect of random selection within the program elements are visualized in Figure~\ref{fig:wlocsel}, and when it is made external to the program elements is visualized in Figure~\ref{fig:wlocsel}.

% ----------------------------------------------------------------------
%\subsubsection{One per element}
%The aim of this criteria is is to take the previous idea to the extreme. We choose only a single mutant per program element.

<<one>>=
#3
@
%\begin{figure*}[t]
%<<one.per.sel.sample,fig.width=10, fig.height=2, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
%o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
%ggplot(subset(o.one, reduction < 100 & (type=='line' | type=='method')), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
%  stat_boxplot(geom ='errorbar')+
%  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none")
%@
%\caption{The effect of one element selection, All are above 0.98 $R^2$.}
%\label{fig:onesel}
%\end{figure*}
%
% ----------------------------------------------------------------------

%\subsection{Operator Selection}
\begin{figure*}[t]
<<op.all,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
#with(subset(stats.df,r.square > 0.9),plot(mutant.reduction, (1-r.square)*100, pch='*', col=as.factor(strategy)))
# "kind" "operator" "s.power" "s.element" "strategy" "mutant.reduction" "sd.reduction"
#  "sample" "r.square" "score.multiplier" "p.value"

@@

\begin{figure*}[t]
<<op.all.2,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
#with(subset(stats.df,r.square > 0.9),plot(mutant.reduction, (1-r.square)*100, pch='*', col=as.factor(strategy)))
# "kind" "operator" "s.power" "s.element" "strategy" "mutant.reduction" "sd.reduction"
#  "sample" "r.square" "score.multiplier" "p.value"

df <-  subset(df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction & mutant.reduction <= 20)
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type))
@
\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only mean reduction <= 20 (5\%)}
\label{fig:fullimgsize2}
\end{figure*}

\begin{figure*}[t]
<<op.all.3,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
#with(subset(stats.df,r.square > 0.9),plot(mutant.reduction, (1-r.square)*100, pch='*', col=as.factor(strategy)))
# "kind" "operator" "s.power" "s.element" "strategy" "mutant.reduction" "sd.reduction"
#  "sample" "r.square" "score.multiplier" "p.value"

@@

\begin{figure*}[t]
<<op.all.4,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
#with(subset(stats.df,r.square > 0.9),plot(mutant.reduction, (1-r.square)*100, pch='*', col=as.factor(strategy)))
# "kind" "operator" "s.power" "s.element" "strategy" "mutant.reduction" "sd.reduction"
#  "sample" "r.square" "score.multiplier" "p.value"

@@

% \begin{figure*}[t]
% <<op.all.2,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% @
% \caption{The mean reduction of mutants vs its standard deviation. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. }
% \end{figure*}
% 
% \begin{figure*}[t]
% <<op.all.4,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=strat, color=mult))
% @
% \caption{The mean reduction of mutants vs its standard deviation. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. The color represents the (1-multiplier) to the sampled mutation score to get final score }
% \end{figure*}
%

% \begin{figure*}[t]
% <<op.all.3,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% dfd <- subset(df, !(strategy %in% c('op','opsel')) )
% ggplot(dfd, aes(sd.reduction, mutant.reduction)) + geom_point(aes(shape=type, color=sqr)) + facet_wrap(~strategy) + theme(axis.text.x = element_text(angle = 90, hjust = 1))
% @
% \label{fig:fullimgshape}
% \end{figure*}
<<opsel>>=
#4
@

%For operator selection, we approximated the operators as far as possible from the research works into the operators exposed by PIT. The results of this are provided in Table~\ref{tbl:opsel}.
% The subsumption graphs are provided in Figure~\ref{fig:subsumptiono}
% TODO : Check if this makes sense.
%\begin{figure*}[t]
%\includegraphics[totalheight=6cm]{fig/original.pdf}
%\caption{Subsumption Original}
%\label{fig:subsumptiono}
%\end{figure*}

%\begin{figure*}[t]
%\includegraphics[totalheight=6cm]{fig/randoop.pdf}
%\caption{Subsumption Randoop}
%\label{fig:subsumptionr}
%\end{figure*}[t]

% ----------------------------------------------------------------------

>>>>

@@

\begin{figure*}[t]
<<x.per.sel.sample,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
ggplot(subset(o.xp.sample, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts + theme(legend.position="none") + opts(title="sample(x)")
o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
ggplot(subset(o.xp.round, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")+ opts(title="sample(x)")

@@

df <- subset(o.xp.opsel, rm.operators <= 20 & reduction != Inf & type != 'operator' & (type != 'n-selection' | rm.operators < 9))
qplot(rm.operators, reduction, fill=interaction(type,rm.operators), data=df, geom="boxplot", position="dodge") + theme_bw()
@
\caption{Operator selection comparison between n-selection and other selection methods in mutation reduction.  We show only up to 8-selection}
\label{fig:xroundsel}
\end{figure*}

\begin{figure*}[t]
<<op.all,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=

@@

\begin{figure*}[t]
<<op.all.2,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
df <-  subset(df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction & mutant.reduction <= 20)
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type))
@
\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only mean reduction <= 20 (5\%)}
\label{fig:fullimgsize2}
\end{figure*}

\begin{figure*}[t]
<<op.all.3,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=

@@

\begin{figure*}[t]
<<op.all.4,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=

@@
